A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-22 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added eth distr multi-run results
added to intro and changed table titles

The nascent field of token engineering is currently establishing its own set 
of tools and processes. As such, ABM lends itself well to analyzing these systems
to support the design process and evaluate system state after launch.

@@

    Using the \textit{linear distribution:}

        \begin{table}[htbp]
            \caption{Lynchpinned Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.006065 &  0.000000 &  0.000000 \\
            \hline
            10 &  0.071656 &  0.009276 &  0.003985 \\
            \hline
            20 &  0.399020 &  0.262837 &  0.177465 \\
            \hline
            \end{tabular}
            \label{lynchpinned_table1}
            \end{center}
        \end{table}

        \begin{table}[htbp]
            \caption{Compromised Groups}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.590035 &  0.435403 &  0.407054 \\
            \hline
            10 &  0.428957 &  0.710509 &  0.536904 \\
            \hline
            20 &  0.557832 &  0.591663 &  0.555565 \\
            \hline
            \end{tabular}
            \label{compromised_table1}
            \end{center}
        \end{table}

        \begin{table}[htbp]
            \caption{Failed Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.0 &  0.0 &  0.0 \\
            \hline
            10 &  0.0 &  0.0 &  0.0 \\
            \hline
            20 &  0.0 &  0.0 &  0.0 \\
            \hline
            \end{tabular}
            \label{failed_table1}
            \end{center}
        \end{table}

        Using the \textit{Ethereum distribution:}

\section{Conclusion and Future work}
\begin{itemize}
\item Dynamic systems -Transfer functions instead of stochastic representations?
\item Utility functions
\item Genetic Algorithms
\item Additional questions
\end{itemize}

>>>>

The nascent field of token engineering is currently establishing its own set 
of tools and processes. As such, ABM lends itself well to analyzing these systems
to support the design process and evaluate system state after launch. In many situations,
agent based modeling maybe the only method to evaluate a cryptoeconomic system as many are
opaque and do not generate significant visible data. Similar to the field of astronomy, an
agent based model could be used to replicate observable system behavior and then infer
causes.

@@

\textit{Group Size} in all distributions group size appears to reduce the percentage
of lynchpinned signatures and compromised groups. why?

\textit{Failure percent}

        \begin{table}[h!]
            \caption{Linear Distribution - Lynchpinned Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.006065 &  0.000000 &  0.000000 \\
            \hline
            10 &  0.071656 &  0.009276 &  0.003985 \\
            \hline
            20 &  0.399020 &  0.262837 &  0.177465 \\
            \hline
            \end{tabular}
            \label{lynchpinned_table1}
            \end{center}
        \end{table}

        \begin{table}[h!]
            \caption{Linear Distribution - Compromised Groups}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.590035 &  0.435403 &  0.407054 \\
            \hline
            10 &  0.428957 &  0.710509 &  0.536904 \\
            \hline
            20 &  0.557832 &  0.591663 &  0.555565 \\
            \hline
            \end{tabular}
            \label{compromised_table1}
            \end{center}
        \end{table}

        \begin{table}[h!]
            \caption{Linear Distribution - Failed Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.0 &  0.0 &  0.0 \\
            \hline
            10 &  0.0 &  0.0 &  0.0 \\
            \hline
            20 &  0.0 &  0.0 &  0.0 \\
            \hline
            \end{tabular}
            \label{failed_table1}
            \end{center}
        \end{table}

        \begin{table}[h!]
            \caption{Ethereum distribution - Lynchpinned Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.011012 &  0.000000 &  0.000000 \\
            \hline
            10 &  0.073725 &  0.025947 &  0.006042 \\
            \hline
            20 &  0.407753 &  0.325947 &  0.203095 \\
            \hline
            \end{tabular}
            \label{lynchpinned_table2}
            \end{center}
        \end{table}

        \begin{table}[h!]
            \caption{Ethereum distribution - Compromised Groups}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.592699 &  0.383390 &  0.394198 \\
            \hline
            10 &  0.566964 &  0.616098 &  0.683071 \\
            \hline
            20 &  0.549456 &  0.526661 &  0.454106 \\
            \hline
            \end{tabular}
            \label{compromised_table2}
            \end{center}
        \end{table}

        \begin{table}[h!]
            \caption{Ethereum distribution - Failed Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.0 &  0.0 &  0.0 \\
            \hline
            10 &  0.0 &  0.0 &  0.0 \\
            \hline
            20 &  0.0 &  0.0 &  0.0 \\
            \hline
            \end{tabular}
            \label{failed_table2}
            \end{center}
        \end{table}

\newpage
\section{Conclusion and Future work}
\begin{itemize}
\item Dynamic systems -Transfer functions instead of stochastic representations?
\item Utility functions
\item Genetic Algorithms
\item Additional questions
\end{itemize}
